### 2013-08-26 tables_and_figures.tex
Updated paper.

\section{Suggested Benchmarks}
\begin{enumerate}
\item
SpMM with 16 floats (or 8 doubles) vectors (will give upper bound in speed). Implement algorithm  from Saul \etal. 
\item
SpMM with 4 floats or 4 doubles (to compare against SpMM). As a precursor to adding more matrices. 
\item
Try to figure out why our performance is so much lower than peak. 
\end{enumerate}

@@

>>>>

\section{Suggested Benchmarks}
\begin{enumerate}
\item
SpMM with 16 floats (or 8 doubles) vectors (will give upper bound in speed). Implement algorithm  from Saul \etal. 
\item
SpMM with 4 floats or 4 doubles (to compare against SpMM). As a precursor to adding more matrices. 
\item
Try to figure out why our performance is so much lower than peak stated in Figure \ref{fig:gflops_peak_per}.
Expecially in the case of compact. To do this, remove permutes, and replace gather by straight forward C++
without using vector notation, but using SIMD commands in addition to OPENPM commands. Make sure we use -O3, and contrast to -O1 and -O2. 
\end{enumerate}

@@

\newfig{figures/test1_readwrite.png}{0.7}{Bandwidth performance under idealized conditions as a function of matrix row size. Entries with "cpp" denote cases where coding was performed without MIC vector instructions.}{fig:band_rw}

\newfig{figures/test1_gather.png}{0.7}{Bandwidth performance under idealized conditions as a function of matrix row size. Entries with "cpp" denote cases where coding was performed without MIC vector      instructions.}{fig:band_gather}

\newfig{figures/test3_gather.png}{0.7}{Bandwidth performance under idealized conditions as a function of matrix row size. Entries with "cpp" denote cases where coding was performed without MIC vector      instructions. The greater speed of the cpp version is obtained throught the use of \#Ivdep {\em and\/} \_\_assumed\_aligned. }{fig:band_gather_ivdep}
